The \dealii Library, Version 9.5

### 2023-06-05 9.5/paper.tex
Minor edits.

Kokkos \cite{trott2022} is a C++ library that enables the creation of
performance portable applications for all major high-performance computing (HPC)
platforms. It implements a programming model that allows developers to write
code that can efficiently run on diverse architectures. Kokkos provides
abstractions for both parallel execution of code and data management. It
supports a wide range of backend programming models, including CUDA, HIP, SYCL,
HPX, OpenMP, and C++ threads, and continues to evolve with the development of
new backend options.

@@

The 9.5 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_4_2_and_9_5_0.html}
{around X incompatible changes}; see \cite{changes95}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority changes internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item
  The class \texttt{hp::DoFHandler} has been removed. The standard \texttt{DoFHandler} now implements all hp-related functionality.

@@

  \item
  This rework also affects the serialization process of active FE indices. You will need to recreate your serialized data \textit{if and only if} you work in hp-mode. You can continue to use previously generated data if you do not use hp-mode. A special case forms \texttt{parallel::distributed::Triangulation} for non-hp data, in which it is sufficient to increase the version in the metadata file by one from ``4'' to ``5''.

>>>>

Kokkos \cite{trott2022} is a C++ library that enables the creation of
performance portable applications for all major high-performance computing (HPC)
platforms. It implements a programming model that allows developers to write
code that can efficiently run on diverse architectures. Kokkos provides
abstractions for both parallel execution of code and data management. It
supports a wide range of backend programming models, including CUDA, HIP, SYCL,
HPX, OpenMP, and C++ threads, and continues to evolve with the development of
new hardware and corresponding backend options.

@@

The 9.5 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_4_2_and_9_5_0.html}
{around X incompatible changes}; see \cite{changes95}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority changes internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item
  The class \texttt{hp::DoFHandler} has been removed. The
  \texttt{DoFHandler} class now implements all $hp$-related
  functionality, as it has for the past few releases.

@@

  \item
  This rework also affects the serialization process of active FE indices. You will need to recreate your serialized data \textit{if and only if} you work in $hp$-mode. You can continue to use previously generated data if you do not use $hp$-mode. A special case forms \texttt{parallel::distributed::Triangulation} for non-$hp$ data, in which it is sufficient to increase the version in the metadata file by one from ``4'' to ``5''.
